Network visualizations

### 2024-02-22 scripts/02.1_visualizeNetworks.qmd
saved seasonal networks with transparent backgrounds

```{r}
#| include: false
load(here("data", "calcSocial", "feedingGraphs.Rda"))
load(here("data", "calcSocial", "flightGraphs.Rda"))
load(here("data", "calcSocial", "roostingGraphs.Rda"))
load(here("data", "calcSocial", "networkMetrics.Rda"))
load(here("data", "mixedModels", "linked.Rda"))

@@

fl_d <- patchwork::wrap_plots(flightPlots_degree, nrow = 3, ncol = 3)
fe_d <- patchwork::wrap_plots(feedingPlots_degree, nrow = 3, ncol = 3)
ro_d <- patchwork::wrap_plots(roostingPlots_degree, nrow = 3, ncol = 3)
ggsave(fl_d, filename = here("fig", "networkGraphs", "seasonal", "degree", "flight.png"), width = 9, height = 7)
ggsave(fe_d, filename = here("fig", "networkGraphs", "seasonal", "degree", "feeding.png"), width = 9, height = 7)
ggsave(ro_d, filename = here("fig", "networkGraphs", "seasonal", "degree", "roosting.png"), width = 9, height = 7)

fl_s <- patchwork::wrap_plots(flightPlots_strength, nrow = 3, ncol = 3)
fe_s <- patchwork::wrap_plots(feedingPlots_strength, nrow = 3, ncol = 3)
ro_s <- patchwork::wrap_plots(roostingPlots_strength, nrow = 3, ncol = 3)
ggsave(fl_s, filename = here("fig", "networkGraphs", "seasonal", "strength", "flight.png"), width = 9, height = 7)
ggsave(fe_s, filename = here("fig", "networkGraphs", "seasonal", "strength", "feeding.png"), width = 9, height = 7)
ggsave(ro_s, filename = here("fig", "networkGraphs", "seasonal", "strength", "roosting.png"), width = 9, height = 7)
```

>>>>

```{r}
#| include: false
load(here("data", "calcSocial", "feedingGraphs.Rda"))
load(here("data", "calcSocial", "flightGraphs.Rda"))
load(here("data", "calcSocial", "roostingGraphs.Rda"))
load(here("data", "calcSocial", "networkMetrics.Rda"))
load(here("data", "mixedModels", "linked.Rda"))
load(here("data/dataPrep/season_names.Rda"))

@@

fl_d <- patchwork::wrap_plots(flightPlots_degree, nrow = 3, ncol = 3)
fe_d <- patchwork::wrap_plots(feedingPlots_degree, nrow = 3, ncol = 3)
ro_d <- patchwork::wrap_plots(roostingPlots_degree, nrow = 3, ncol = 3)
ggsave(fl_d, filename = here("fig", "networkGraphs", "seasonal", "degree", "flight.png"), width = 9, height = 7, bg = "transparent")
ggsave(fe_d, filename = here("fig", "networkGraphs", "seasonal", "degree", "feeding.png"), width = 9, height = 7, bg = "transparent")
ggsave(ro_d, filename = here("fig", "networkGraphs", "seasonal", "degree", "roosting.png"), width = 9, height = 7, bg = "transparent")

fl_s <- patchwork::wrap_plots(flightPlots_strength, nrow = 3, ncol = 3)
fe_s <- patchwork::wrap_plots(feedingPlots_strength, nrow = 3, ncol = 3)
ro_s <- patchwork::wrap_plots(roostingPlots_strength, nrow = 3, ncol = 3)
ggsave(fl_s, filename = here("fig", "networkGraphs", "seasonal", "strength", "flight.png"), width = 9, height = 7, bg = "transparent")
ggsave(fe_s, filename = here("fig", "networkGraphs", "seasonal", "strength", "feeding.png"), width = 9, height = 7, bg = "transparent")
ggsave(ro_s, filename = here("fig", "networkGraphs", "seasonal", "strength", "roosting.png"), width = 9, height = 7, bg = "transparent")
```
